---
title: "Untitled"
author: "Shylock"
date: "12/17/2020"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE, warning=FALSE, comment= FALSE, }
knitr::opts_chunk$set(echo = FALSE)
# library(qcoder)
library(tidyverse)
library(janitor)
library(bbplot)
library(gt)
suppressWarnings(library(readxl))
library(knitr)



```

# All donor funded programs
```{r, results='asis', message=FALSE, warning=FALSE}


clean_data <- read_excel("NGO EXCEL.xlsx",
                         col_types = c("text", "text", "text",
                                       "text", "text", "numeric")) %>%
  clean_names()

data <-
  clean_data %>%
  group_by(development, date) %>%
  tally() %>%
  arrange(desc(n)) %>%
  pivot_wider(names_from = date, values_from = n)
kable(data)

```

# All funding by years
```{r}
summ1 <- clean_data %>%
  group_by(date, development) %>%
  summarise(budget = sum(project_budget)) %>%
  pivot_wider(names_from = date,
              values_from = budget,
              values_fill = 0)
kable(summ1)
```
# Social Protection (N)

```{r}
sp <- clean_data %>%
  filter(nexus == "Social protection")

sp_n <- sp %>%
  group_by(date, development, project_status) %>%
  tally() %>%
  pivot_wider(names_from = project_status,
              values_from = n,
              values_fill = 0)
kable(sp_n)
```

# Social protection (Value)
```{r}
sp_v <- clean_data %>%
  filter(nexus == "Social protection") %>%
  group_by(date, development) %>%
  summarise(budget = sum(project_budget)) %>%
  pivot_wider(names_from = date,
              values_from = budget,
              values_fill = 0)
kable(sp_v)
```


# Resilience (N)

```{r}
resilence <- clean_data %>%
  filter(nexus == "Resilience Humanitarian and Development")

a <- resilence %>%
  group_by(date, development, project_status) %>%
  tally() %>%
  pivot_wider(names_from = project_status,
              values_from = n,
              values_fill = 0)
kable(a)
```


# Resilience (Value)

```{r}
res_v <- clean_data %>%
  filter(nexus == "Resilience Humanitarian and Development") %>%
  group_by(date, development) %>%
  summarise(budget = sum(project_budget)) %>%
  pivot_wider(names_from = date,
              values_from = budget,
              values_fill = 0)
kable(res_v)
```



# Governance(N)

```{r}
gov <- clean_data %>%
  filter(nexus == "GOVernance, human rights, democracy and rule of law")

a <- gov %>%
  group_by(date, development, project_status) %>%
  tally() %>%
  pivot_wider(names_from = project_status,
              values_from = n,
              values_fill = 0)
kable(a)
```


# Governance (Value)

```{r}
gov_v <- clean_data %>%
  filter(nexus == "GOVernance, human rights, democracy and rule of law") %>%
  group_by(date, development) %>%
  summarise(budget = sum(project_budget)) %>%
  pivot_wider(names_from = date,
              values_from = budget,
              values_fill = 0)
kable(gov_v)
```



# Agriculture and climate change (N)

```{r}
agric <- clean_data %>%
  filter(nexus == "Agriculture and climate change")

a <- agric %>%
  group_by(date, development, project_status) %>%
  tally() %>%
  pivot_wider(names_from = project_status,
              values_from = n,
              values_fill = 0)
kable(a)
```


# Agriculture and climate change (Value)

```{r}
agric_v <- clean_data %>%
  filter(nexus == "Agriculture and climate change") %>%
  group_by(date, development) %>%
  summarise(budget = sum(project_budget)) %>%
  pivot_wider(names_from = date,
              values_from = budget,
              values_fill = 0)
kable(agric_v)
```


#  Natural resources management (N)

```{r}
nrm <- clean_data %>%
  filter(nexus == "Natural resources management")

a <- nrm %>%
  group_by(date, development, project_status) %>%
  tally() %>%
  pivot_wider(names_from = project_status,
              values_from = n,
              values_fill = 0)
kable(a)
```


# Natural resources management (Value)

```{r}
nrm_v <- clean_data %>%
  filter(nexus == "Natural resources management") %>%
  group_by(date, development) %>%
  summarise(budget = sum(project_budget)) %>%
  pivot_wider(names_from = date,
              values_from = budget,
              values_fill = 0)
kable(nrm_v)
```

#  Education sector (N)

```{r}
edu <- clean_data %>%
  filter(nexus == "Education sector")

a <- edu %>%
  group_by(date, development, project_status) %>%
  tally() %>%
  pivot_wider(names_from = project_status,
              values_from = n,
              values_fill = 0)
kable(a)
```


# Education sector (Value)

```{r}
edu_v <- clean_data %>%
  filter(nexus == "Education sector") %>%
  group_by(date, development) %>%
  summarise(budget = sum(project_budget)) %>%
  pivot_wider(names_from = date,
              values_from = budget,
              values_fill = 0)
kable(edu_v)
```

#   Gender issues (N)

```{r}
gen <- clean_data %>%
  filter(nexus == "Gender issues")

a <- gen %>%
  group_by(date, development, project_status) %>%
  tally() %>%
  pivot_wider(names_from = project_status,
              values_from = n,
              values_fill = 0)
kable(a)
```


#  Gender issues (Value)

```{r}
gen_v <- clean_data %>%
  filter(nexus == "Gender issues") %>%
  group_by(date, development) %>%
  summarise(budget = sum(project_budget)) %>%
  pivot_wider(names_from = date,
              values_from = budget,
              values_fill = 0)
kable(gen_v)
```

#   Health sector (N)

```{r}
heal <- clean_data %>%
  filter(nexus == "Health sector")

a <- heal %>%
  group_by(date, development, project_status) %>%
  tally() %>%
  pivot_wider(names_from = project_status,
              values_from = n,
              values_fill = 0)
kable(a)
```


#  Health sector (Value)

```{r, echo= FALSE}
heal_v <- clean_data %>%
  filter(nexus == "Health sector") %>%
  group_by(date, development) %>%
  summarise(budget = sum(project_budget)) %>%
  pivot_wider(names_from = date,
              values_from = budget,
              values_fill = 0)
kable(heal_v)
```


#   Private sector and trade (N)

```{r}
pvt <- clean_data %>%
  filter(nexus == "Private sector and trade")

a <- pvt %>%
  group_by(date, development, project_status) %>%
  tally() %>%
  pivot_wider(names_from = project_status,
              values_from = n,
              values_fill = 0)
kable(a)
```


#  Private sector and trade (Value)

```{r, echo= FALSE}
pvt_v <- clean_data %>%
  filter(nexus == "Private sector and trade") %>%
  group_by(date, development) %>%
  summarise(budget = sum(project_budget)) %>%
  pivot_wider(names_from = date,
              values_from = budget,
              values_fill = 0)
kable(pvt_v)
```


#   SMEs and employment creation (N)

```{r}
sme <- clean_data %>%
  filter(nexus == "SMEs and employment creation")

a <- sme %>%
  group_by(date, development, project_status) %>%
  tally() %>%
  pivot_wider(names_from = project_status,
              values_from = n,
              values_fill = 0)
kable(a)
```


#  SMEs and employment creation (Value)

```{r, echo= FALSE}
sme_v <- clean_data %>%
  filter(nexus == "SMEs and employment creation") %>%
  group_by(date, development) %>%
  summarise(budget = sum(project_budget)) %>%
  pivot_wider(names_from = date,
              values_from = budget,
              values_fill = 0)
kable(sme_v)
```